---
title: 'Topic: Women’s political participation and health'
author: "Andreas Felderer"
output:
  pdf_document: default
  pdf: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Setup

```{r, results='hide', message=FALSE}
library(tidyverse) 
library(gtsummary) # descriptive statistics
library(modelsummary) # alternative to stargazer
library(estimatr) # regressions with robust SE
library(knitr) # data frames as latex tables

df <- read.csv("political_participation.csv", header = T)
```

```{r}
names(df)
summary(df)
```

```{r}
df %>% 
  select(quota_sample, country_name, Wanted_TFR) %>% 
  unique()
```

### How: Do a systematic regression analysis to answer the research question. You will find the dataset

#### The dependent variables for your analysis are:

-    maternal mortality (MMR_WDI),

-   child mortality (I5M_WDI)

-   fertility (TFR_WDI).

The main independent variable is whether the country has

-   introduced a quota (quota),

-   the year of the introduction (quotayear),

-   the share of women in parliament(women_parliament).

#### Start with some descriptive statistics.

-   Do a systematic regression analysis to answer the research question using the appropriate methodological approach.

-   The regression analysis should include a systematic analysis of the effect of the quota introduction on maternal mortality, child mortality and fertility.

-   Begin your regression analysis by modelling maternal mortality as it is done in Table A2 in the paper (see the notes of the Tables for a description of the approach).

-   Do the same analysis for child mortality and fertility.

    -   You can start with a base-model (single regressor)

    -   and then extend the model to other control variables in the data you think that would be important to take into account.

    -   You can also work with non-linearities and interaction terms to answer the research question.

-   Do the analysis separately for female and male child mortality (I5M_M\_WDI, I5M_F\_DI).

-   You don't need to do an event study (but you can try if you want to).

-   Use a similar IV approach to produce results as shown in table A4 in the paper. Explain the choice of the IV variable and discuss whether you think that the IV a valid.

-   Interpret the regression results with respect to:

    -    the significance of the estimated effects,

    -   their economic meaning

    -   and also with respect to the model performance.

-   Discuss your results from an economic standpoint.
