---
title: 'Topic: Women’s political participation and health'
author: "Andreas Felderer"
output:
  pdf_document: default
  pdf: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Woman's political participation and health

## Empirical problem:

What is the relationship between women's political participation and health?

## Policy question:

Do quotas of parliament seats for women increase the health of women and children?

## Task: Analyze the effect of the introduction of quotas for women in parliament seats on women's and child health.

## Background:

Maternal and child mortality as well as high fertility rates are a major concern in many low-and middle-income countries. In a recent study,Sonia Bhalotra and colleagues (see below) study the effect of increased female political participation on maternal mortality. In doing so, the authors use a novel data set on the introduction of quotas for women in parliament across the world and combine this data with information on women's health. They find that the introduction of quotas for women in parliament results in a 9 to 12%decline in maternal mortality. In this project, you will extend this study by also looking on the effect of women's political participation on child health and fertility. For this you will work with data from the World Development Indicators. You will work with different methods, including panel, diff-in-diff and IV regression.

### Setup

```{r, results='hide', message=FALSE}
library(tidyverse) 
library(gtsummary) # descriptive statistics
library(modelsummary) # alternative to stargazer
library(estimatr) # regressions with robust SE
library(knitr) # data frames as latex tables
library(car)
library(kableExtra)
library(tibble)
```


```{r, results='hide', message=FALSE}
df <- read.csv("political_participation.csv", header = T, stringsAsFactors = T)
```

### How: Do a systematic regression analysis to answer the research question.

#### The dependent variables for your analysis are:

-   maternal mortality (MMR_WDI),

```{r mmr summary}
summary(df$MMR_WDI)
print("N:")
length(df$MMR_WDI)
```

```{r mmr include=FALSE}
df %>% 
  ggplot(aes(x=MMR_WDI, y=after_stat(count)
             )
         ) +
  geom_histogram() +
  labs(x = "Maternal Mortality Ratio", y = "Count") +
  ggtitle(expression(atop("Maternal Mortality Ratio"))) +
  scale_fill_viridis_d()
ggsave("figures/Maternal_Mortality.png")
```

```{r log mmr include=FALSE}
df %>% 
  ggplot(aes(x=log(MMR_WDI), y=after_stat(count)
             )
         ) +
  geom_histogram() +
  labs(x = "Log Maternal Mortality Ratio", y = "Count") +
  ggtitle(expression(atop("Log Maternal Mortality Ratio"))) +
  scale_fill_viridis_d()
ggsave("figures/Log_Maternal_Mortality.png")
```

Comment MMR_WDI is only measured after 2000!


-   child mortality (I5M_WDI)

```{r i5m include=FALSE}
df %>% 
  ggplot(aes(x=I5M_WDI, y=after_stat(count)
             )
         ) +
  geom_histogram() +
  labs(x = "Child Mortality before 5", y = "Count") +
  ggtitle(expression(atop("Child Mortality before 5",))) +
  scale_fill_viridis_d()
#ggsave("figures/Child_Mortality.png")
```

```{r  log i5m include=FALSE}
df %>% 
  ggplot(aes(x=log(I5M_WDI), y=after_stat(count)
             )
         ) +
  geom_histogram() +
  labs(x = "Log Child Mortality before 5", y = "Count") +
  ggtitle(expression(atop("Log Child Mortality before 5",))) +
  scale_fill_viridis_d()
#ggsave("figures/Log_Child_Mortality.png")
```

-   fertility (TFR_WDI).

```{r tfr include=FALSE}
df %>% 
  filter(year != 2018) %>% 
  ggplot(aes(x=TFR_WDI, y=after_stat(count)
             )
         ) +
  geom_histogram(bins=50) +
  labs(x = "Total Fertility Rate", y = "") +
  ggtitle(expression(atop("Total Fertility Rate", atop(italic("w/o 2018"), "")))) +
  scale_fill_viridis_d()
ggsave("figures/Total_Fertility_Rate.png")

```

```{r log tfr include=FALSE}
df %>% 
  filter(year != 2018) %>% 
  ggplot(aes(x=log(TFR_WDI), y=after_stat(count)
             )
         ) +
  geom_histogram(bins=50) +
  labs(x = "Log Total Fertility Rate", y = "") +
  ggtitle(expression(atop("Log Total Fertility Rate", atop(italic("w/o 2018"), "")))) +
  scale_fill_viridis_d()
ggsave("figures/Log_Total_Fertility_Rate.png")
```

TFR is missing in 2018

The main independent variable is

-   whether the country has introduced a quota (quota),

```{r Quota over time include=FALSE}
df %>% 
  group_by(year) %>% 
  summarise(quota_perc = mean(quota)) %>% 
  ggplot(aes(x=year, y=quota_perc)) +
    geom_line() +
    coord_cartesian(ylim = c(0,1)) + 
    labs(x = "", y = "Portion of Countries with a Quota", title = "Women Quota over Time") +
    scale_fill_viridis_d()
ggsave("figures/Women_Quota_over_Time.png")
```

```{r Variables time include=FALSE}
df %>% 
  group_by(year) %>% 
  filter(complete.cases(MMR_WDI), complete.cases(I5M_WDI), complete.cases(women_parliament),
         complete.cases(gdp_pc)) %>% 
  summarise(mmr = mean(MMR_WDI), tfr = mean(TFR_WDI), i5m = mean(I5M_WDI), 
            gdp = mean(gdp_pc), wp = mean(women_parliament) ) %>% 
  mutate(mmr = mmr/max(mmr), tfr = tfr/max(tfr), i5m = i5m/max(i5m), gdp = gdp/max(gdp), wp = wp/max(wp)) %>% 
  ggplot() +
    geom_line(aes(x=year, y=mmr, 
                  color = "Maternal Mortatily Ratio",
                  linetype = "Maternal Mortatily Ratio")) +
    geom_line(aes(x=year, y=tfr, 
                  color = "Total Fertility Rate", 
                  linetype = "Total Fertility Rate")) +
    geom_line(aes(x=year, y=i5m, 
                  color = "Child Mortality before 5", 
                  linetype = "Child Mortality before 5")) +
    geom_line(aes(x=year, y=gdp, 
                  color = "Gross Domestic Product", 
                  linetype = "Gross Domestic Product")) + 
    geom_line(aes(x=year, y=wp, 
                  color = "Percent of Women in Parliament", 
                  linetype = "Percent of Women in Parliament")) + 
    coord_cartesian(ylim = c(0,1)) +
    labs(x = "", y = "Yearly mean scaled by all time maximum", title = "Time Development of Variables of Interest", linetype = "Variables", color = "Variables") +
    scale_fill_viridis_d()
ggsave("figures/Time_Variables.png")
```

```{r variables time scaled include=FALSE}
df %>% 
  group_by(year) %>% 
  filter(complete.cases(I5M_WDI), complete.cases(women_parliament)) %>% 
  summarise(i5m_f = mean(I5M_F_WDI), i5m_m = mean(I5M_M_WDI), i5m = mean(I5M_WDI)
            , wp = mean(women_parliament) ) %>% 
  mutate(i5m_f = i5m_f/max(i5m_f), i5m_m = i5m_m/max(i5m_m), i5m = i5m/max(i5m), wp = wp/max(wp)) %>%
  ggplot() +
    geom_line(aes(x=year, y=i5m_f, 
                  color = "Female Child Mortality before 5", 
                  linetype = "Female Child Mortality before 5")) +
    geom_line(aes(x=year, y=i5m_m, 
                  color = "Male Child Mortality before 5", 
                  linetype = "Male Child Mortality before 5")) +
    geom_line(aes(x=year, y=wp, 
                  color = "Percent of Women in Parliament", 
                  linetype = "Percent of Women in Parliament")) + 
    labs(x = "", y = "Yearly mean scaled by all time maximum", title = "Time Development of Variables of Interest", linetype = "Variables", color = "Variables") +
    scale_fill_viridis_d()
ggsave("figures/Time_Variables_scaled.png")
```

```{r Male vs female i5m}
df %>% 
  group_by(year) %>% 
  filter(complete.cases(I5M_F_WDI), complete.cases(I5M_M_WDI)) %>% 
  summarise(i5mm = mean(I5M_M_WDI), i5mf = mean(I5M_F_WDI), i5m = mean(I5M_WDI)) %>% 
  ggplot() +
    geom_line(aes(x=year, y=i5mm, 
                  color = "Male Child Mortality before 5",
                  linetype = "Male Child Mortality before 5")) +
    geom_line(aes(x=year, y=i5mf, 
                  color = "Female Child Mortality before 5", 
                  linetype = "Female Child Mortality before 5")) +
    geom_line(aes(x=year, y=i5m, 
                  color = "Child Mortality before 5", 
                  linetype = "Child Mortality before 5")) +
    labs(x = "", y = "Yearly Mean", title = "Time Development of Child Mortality", linetype = "Variables", color = "Variables") +
    scale_fill_viridis_d()
ggsave("figures/Time_I5m.png")
```


-   the year of the introduction (quotayear),

```{r include=FALSE}
df %>% 
  select(year) %>% 
  unique() %>% 
  count() -> n_years

df %>% 
  filter(complete.cases(quotayear)) %>% 
  ggplot(aes(x=quotayear, 
             y=after_stat(count/n_years$n)
             )
         ) +
  geom_histogram(binwidth = 1) +
  labs(x = "Year", y = "Count of Countries") +
  ggtitle(expression(atop("Introduction of Women Quotas in Parliament"))) +
  scale_fill_viridis_d()
ggsave("figures/Quota_Introduction.png")
```

-   the share of women in parliament(women_parliament).

```{r  message=FALSE, include=FALSE}
df %>% 
  group_by(year) %>% 
  filter(complete.cases(women_parliament)) %>% 
  summarise(parl_share = mean(women_parliament)/100) %>% 
  ggplot(aes(x=year, y=parl_share)) +
    geom_line() +
    annotate("rect", xmin = 1991, xmax = 1997, ymin = 0, ymax = 1, alpha = .5) +
    coord_cartesian(ylim = c(0,0.5)) + 
    labs(x = "Year", y = "Average share of Women in Parliaments", title = "Average share of Women in Parliament over Time") +
    scale_fill_viridis_d()
ggsave("figures/Share_Women_in_Parliament.png")
```

### Variables:

-   MMR_WDI is only measured after 2000!

-   Child mortality (I5M_WDI) 161 missing values (countries with missing values seem to have a slight skew towards higher child mortality compared to other countries) apparently completely missing: Puerto Rico, Kosovo & Greenland -\> 44 remaining most of which are at the beginning of the data (i.e. 1980 ff.)

-   Fertitilty (TFR_WDI) -\> 2018 not measured + 31 missing values (Kosovo 1980, Serbia 1980 - 1999, Seyshelles 1980-1996)

# Maternal Mortality

```{r df_w}
df %>% 
  filter(country_name != "India", country_name != "China") -> df_w
```

```{r cpi gender}
df %>% 
  filter(complete.cases(cpia_gender), gdp_pc > 10000) %>% 
  select(country_name, gdp_pc) %>% 
  unique()
```

```{r table style}
coef_map = c("log(gdp_pc)"="ln(GDP per Capita)",
             "women_parliament" = "SWP", 
             "quota" = "Quota Dummy", 
             "lag(quota, 2)" = "Lagged Quota (2Y)",
             "lag(quota, 1)" = "Lagged Quota (1Y)",
             "lag(women_parliament, 1)" = "Lagged SWP (1Y)",
             "I5M_WDI" = "I5M",
             "EDU_PRIM_WDI" = "Completed Prim. Educ.", 
             "EDU_PRIM_F_WDI" = "Female Prim. Educ.", 
             "EDU_PRIM_M_WDI" = "Male Prim. Educ.", 
             "HEA_EXP" = "Health Exp. perc. of GDP",
             "cpia_gender" = "Gender Policy in Place",
             "log(gdp_pc * HEA_EXP)" = "ln(Absolute Health Exp. per Capita)")

gm_map <- list(
  list("raw" = "nobs", "clean" = "N", "fmt" = 0),
  list("raw" = "r.squared", "clean" = "R2", "fmt" = 2),
  list("raw" = "adj.r.squared", "clean" = "R2 Adj.", "fmt" = 2))

stat_map = c("conf.int")
```

## Base

```{r mmr base}
models_mmr <- list()

models_mmr[["(1)"]] <- lm_robust(
  women_parliament ~ log(gdp_pc) + lag(quota, 1),
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr[["(2)"]] <- lm_robust(
  women_parliament ~ log(gdp_pc) + lag(quota, 1),
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr[["(3)"]] <- lm_robust(
  women_parliament ~ log(gdp_pc) + lag(quota, 1),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr[["(4)"]] <- lm_robust(
  MMR_WDI ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr[["(5)"]] <- lm_robust(
  MMR_WDI ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr[["(6)"]] <- lm_robust(
  MMR_WDI ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr[["(7)"]] <- lm_robust(
  log(MMR_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr[["(8)"]] <- lm_robust(
  log(MMR_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr[["(9)"]] <- lm_robust(
  log(MMR_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")


#### Style of the Table
rows <- tribble(~term,             ~first,  ~sec, ~th, ~four, ~five, ~six, ~sev, ~eig, ~nin,
                'Exclude CN + IN',   ' ' ,   '*', '*',   ' ',   '*',  '*',  ' ',  '*', '*',
                'Population Weights',' ' ,   ' ', '*',   ' ',   ' ',  '*',  ' ',  ' ', '*')

attr(rows, 'position') <- c(7,8)

modelsummary(
  models_mmr, 
  fmt = 2,
  stars = T, 
  title = "Reproducing Results of \\citep{bhalotra_maternal_2018}  \\label{tab:reprod}",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = F,
  add_rows = rows,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  add_header_above(c(" " = 1, "% of Women in Parliament" = 3, "Maternal Mortality Ratio" = 3, "ln(Maternal Mortality Ratio)" = 3)) %>% 
  footnote("All models include country and year fixed effects. Standard errors clustered by country, and 95% confidence intervals are presented in square brackets.") %>% 
  kable_styling(full_width = T) %>% 
  column_spec(1, width="60pt")  %>% save_kable("tables/MMR_base.tex")
```

## Controls
```{r}
models_control <- list()
```

```{r mmr controls}
models_mmr_cont <- list()

models_mmr_cont[["ln(MMR) Base"]] <- lm_robust(
  log(MMR_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr_cont[["ln(MMR) Gender Policy"]] <- lm_robust(
  log(MMR_WDI) ~  log(gdp_pc) + lag(quota, 2) + cpia_gender,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr_cont[["ln(MMR) Health Expenditure"]] <- lm_robust(
  log(MMR_WDI) ~  log(gdp_pc) + lag(quota, 2) + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr_cont[["ln(MMR) Prim. Educ."]] <- lm_robust(
  log(MMR_WDI) ~  log(gdp_pc) + lag(quota, 2) + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr_cont[["ln(MMR) Full"]] <- lm_robust(
  log(MMR_WDI) ~  log(gdp_pc) + lag(quota, 2) + cpia_gender +  HEA_EXP + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_mmr_cont[["Placebo: ln(GDP)"]] <- lm_robust(
  log(gdp_pc) ~ lag(quota, 2) + HEA_EXP + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0") 

models_control[["ln(MMR)"]] <- models_mmr_cont[["ln(MMR) Full"]]

modelsummary(
  models_mmr_cont, 
  fmt = 2,
  stars = T, 
  title = "ln(Maternal Mortality Ratio) with Controls",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  #format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  kable_styling(full_width = T) %>% 
  column_spec(1, width="60pt") #%>% save_kable("tables/additional/MMR_controls.tex")
```

# IV

```{r hypothesis}
library(AER)
relevance <- list()

print("Full data NO population weights")
relevance[["Base"]] <- lm_robust(women_parliament ~ lag(quota,1),
                                     clusters = dhscc3, 
                                     fixed_effects = year + dhscc3, 
                                     se_type = "CR0",
                                     data=df)

print("Full data WITH population weights")
relevance[["Weights"]] <- lm_robust(women_parliament ~ lag(quota,1),
                                     weights = pop, 
                                     clusters = dhscc3, 
                                     fixed_effects = year + dhscc3, 
                                     se_type = "CR0",
                                     data=df)

summary(relevance[["Weights"]])
print("Data with China and India removed and WITH population weights")
relevance[["Weights ex. CN + IN"]] <- lm_robust(women_parliament ~ lag(quota,1),
                                                 weights = pop, 
                                                 data=df_w, 
                                                 clusters = dhscc3, 
                                                 fixed_effects = year + dhscc3, 
                                                 se_type = "CR0")

rows <- tribble(~term,    ~first,  ~sec, ~th, 
                'Proj. F',  toString(round(relevance[["Base"]]$proj_fstatistic[1], 3) ),
                toString(round(relevance[["Weights"]]$proj_fstatistic[1],3) ), 
                toString(round(relevance[["Weights ex. CN + IN"]]$proj_fstatistic[1],3) )  )
attr(rows, 'position') <- c(3)

gm <- gm_map <- list(
  list("raw" = "nobs", "clean" = "N", "fmt" = 0),
  list("raw" = "r.squared", "clean" = "R2", "fmt" = 2),
  list("raw" = "adj.r.squared", "clean" = "R2 Adj.", "fmt" = 2))

modelsummary(relevance, 
  fmt = 3,
  stars = T, 
  title = "Relevance of the Instrument for SWP",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm,
  escape = FALSE,
  add_rows = rows,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% save_kable("tables/IV_Relevance.tex")
```

The instrument is not Weak!

```{r iv base}
models_iv <- list()

models_iv[["(1)"]] <- iv_robust(
  MMR_WDI ~ log(gdp_pc) + HEA_EXP + EDU_PRIM_WDI + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + 
    HEA_EXP + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv[["(2)"]] <- iv_robust(
  MMR_WDI ~ log(gdp_pc) + HEA_EXP + EDU_PRIM_WDI + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + 
    HEA_EXP + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv[["(3)"]] <- iv_robust(
  MMR_WDI ~ log(gdp_pc) +  HEA_EXP + EDU_PRIM_WDI + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) +
    HEA_EXP + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv[["(4)"]] <- iv_robust(
  TFR_WDI ~ log(gdp_pc) + EDU_PRIM_WDI + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI + 
    HEA_EXP,
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv[["(5)"]] <- iv_robust(
  TFR_WDI ~ log(gdp_pc) + EDU_PRIM_WDI + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI + 
    HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv[["(6)"]] <- iv_robust(
  TFR_WDI ~ log(gdp_pc) + EDU_PRIM_WDI + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI + 
    HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv[["(7)"]] <- iv_robust(
  I5M_WDI ~  log(gdp_pc) + EDU_PRIM_WDI  + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI  +
    HEA_EXP,
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv[["(8)"]] <- iv_robust(
  I5M_WDI ~  log(gdp_pc) + EDU_PRIM_WDI  + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI  +
    HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv[["(9)"]] <- iv_robust(
  I5M_WDI ~  log(gdp_pc) + EDU_PRIM_WDI  + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI  +
    HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

#### Style of the Table
rows <- tribble(~term,             ~first,  ~sec, ~th, ~four, ~five, ~six, ~sev, ~eig, ~nin,
                'Exclude CN + IN',   ' ' ,   '*', '*',   ' ',   '*',  '*',  ' ',  '*', '*',
                'Population Weights',' ' ,   ' ', '*',   ' ',   ' ',  '*',  ' ',  ' ', '*')

attr(rows, 'position') <- c(5,6)

modelsummary(
  models_iv,
  fmt = 2 ,
  stars = T, 
  title = "IV Base Model",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  add_rows = rows,
  #format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  add_header_above(c(" " = 1, "Maternal Mortality Rate" = 3, "Total Fertility Rate" = 3, "Child Mortality" = 3)) %>% 
  kable_styling(full_width = T) %>% 
  column_spec(1, width="60pt") #%>% save_kable("tables/addidtional/IV_base.tex")
```

```{r iv ln base}
models_iv_ln <- list()

models_iv_ln[["(1)"]] <- iv_robust(
  log(MMR_WDI) ~ log(gdp_pc) + HEA_EXP + EDU_PRIM_WDI + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + 
    HEA_EXP + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv_ln[["(2)"]] <- iv_robust(
  log(MMR_WDI) ~ log(gdp_pc) + HEA_EXP + EDU_PRIM_WDI + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + 
    HEA_EXP + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv_ln[["(3)"]] <- iv_robust(
  log(MMR_WDI) ~ log(gdp_pc) + HEA_EXP + EDU_PRIM_WDI + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + 
    HEA_EXP + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv_ln[["(4)"]] <- iv_robust(
  log(TFR_WDI) ~ log(gdp_pc) + EDU_PRIM_WDI + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI + 
    HEA_EXP,
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv_ln[["(5)"]] <- iv_robust(
  log(TFR_WDI) ~ log(gdp_pc) + EDU_PRIM_WDI + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI + 
    HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv_ln[["(6)"]] <- iv_robust(
  log(TFR_WDI) ~ log(gdp_pc) + EDU_PRIM_WDI + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI + 
    HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv_ln[["(7)"]] <- iv_robust(
  log(I5M_WDI) ~ log(gdp_pc) + EDU_PRIM_WDI  + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI  +
    HEA_EXP,
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv_ln[["(8)"]] <- iv_robust(
  log(I5M_WDI) ~  log(gdp_pc) + EDU_PRIM_WDI  + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI  +
    HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_iv_ln[["(9)"]] <- iv_robust(
  log(I5M_WDI) ~  log(gdp_pc) + EDU_PRIM_WDI  + HEA_EXP + 
    lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_WDI  +
    HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

#### Style of the Table
rows <- tribble(~term,             ~first,  ~sec, ~th, ~four, ~five, ~six, ~sev, ~eig, ~nin,
                'Exclude CN + IN',   ' ' ,   '*', '*',   ' ',   '*',  '*',  ' ',  '*', '*',
                'Population Weights',' ' ,   ' ', '*',   ' ',   ' ',  '*',  ' ',  ' ', '*')

attr(rows, 'position') <- c(9,10)

modelsummary(
  models_iv_ln,
  fmt = 2,
  stars = T, 
  title = "",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  add_rows = rows,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  add_header_above(c(" " = 1, "ln(Maternal Mortality Rate)" = 3, "ln(Total Fertility Rate)" = 3, "ln(Child Mortality)" = 3)) %>% 
  kable_styling(full_width = T) %>% 
  column_spec(1, width="60pt")  %>% save_kable("tables/additional/IV_LN_base.tex")
```

```{r iv reduced}
iv_models <- list()
iv_models[["IV ln(MMR)"]] <- models_iv_ln[["(3)"]]
iv_models[["IV ln(TFR)"]] <- models_iv_ln[["(6)"]]
iv_models[["IV ln(I5M)"]] <- models_iv_ln[["(9)"]]

modelsummary(
  iv_models,
  fmt = 3,
  stars = T, 
  title = "IV Regression (with population weights excluding China and India and quota as instrument)",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  #format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  kable_styling(full_width = T) %>% 
  column_spec(1, width="60pt") # %>% save_kable("tables/IV.tex")
```


### Complete MMR
```{r mmr complete}
mmr_comp <- list()

mmr_comp[["MMR"]] <- models_mmr[["(6)"]]
mmr_comp[["ln(MMR) Base"]] <- models_mmr[["(9)"]]
mmr_comp[["ln(MMR) Cont. 1"]] <- models_mmr_cont[["ln(MMR) Gender Policy"]]
mmr_comp[["ln(MMR) Cont. 2"]] <- models_mmr_cont[["ln(MMR) Health Expenditure"]]
mmr_comp[["ln(MMR) Cont. 3"]] <- models_mmr_cont[["ln(MMR) Prim. Educ."]]
mmr_comp[["ln(MMR) Full"]] <- models_mmr_cont[["ln(MMR) Full"]]
mmr_comp[["IV MMR"]] <- models_iv[["(3)"]]
mmr_comp[["IV ln(MMR)"]] <- models_iv_ln[["(3)"]]
mmr_comp[["Placebo: ln(GDP)"]] <- models_mmr_cont[["Placebo: ln(GDP)"]]


modelsummary(
  mmr_comp,
  fmt = 2,
  stars = T, 
  title = "Maternal Mortality Ratio (with country weights exlcuding China and India)",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  kable_styling(full_width = T) %>% 
  footnote("All models include country and year fixed effects. Standard errors clustered by country, and 95% confidence intervals are presented in square brackets.") %>% 
  column_spec(1, width="60pt")  %>% save_kable("tables/MMR_complete.tex")
```

# Fertility

## Base

```{r tfr base}
models_tfr <- list()

models_tfr[["(1)"]] <- lm_robust(
  women_parliament ~ log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr[["(2)"]] <- lm_robust(
  women_parliament ~ log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr[["(3)"]] <- lm_robust(
  women_parliament ~ log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr[["(4)"]] <- lm_robust(
  TFR_WDI ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr[["(5)"]] <- lm_robust(
  TFR_WDI ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr[["(6)"]] <- lm_robust(
  TFR_WDI ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr[["(7)"]] <- lm_robust(
  log(TFR_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr[["(8)"]] <- lm_robust(
  log(TFR_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr[["(9)"]] <- lm_robust(
  log(TFR_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

#### Style of the Table
rows <- tribble(~term,             ~first,  ~sec, ~th, ~four, ~five, ~six, ~sev, ~eig, ~nin,
                'Exclude CN + IN',   ' ' ,   '*', '*',   ' ',   '*',  '*',  ' ',  '*', '*',
                'Population Weights',' ' ,   ' ', '*',   ' ',   ' ',  '*',  ' ',  ' ', '*')

attr(rows, 'position') <- c(5,6)

modelsummary(
  models_tfr, 
  fmt = 2,
  stars = T, 
  title = "Total Fertility Rate",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  add_rows = rows,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  add_header_above(c(" " = 1, "% of Women in Parliament" = 3, "Total Fertitily Rate" = 3, "ln(Total Fertitily Rate)" = 3)) %>% 
  kable_styling(full_width = T) %>% 
  column_spec(1, width="60pt") %>% save_kable("tables/additional/TFR_base.tex")
```

## Controls

```{r tfr controls}
models_tfr_cont <- list()

models_tfr_cont[["ln(TFR)"]] <- lm_robust(
  log(TFR_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr_cont[["ln(TFR)  Gender Policy"]] <- lm_robust(
  log(TFR_WDI) ~  log(gdp_pc) + lag(quota, 2) + cpia_gender,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr_cont[["ln(TFR) Health Expenditure"]] <- lm_robust(
  log(TFR_WDI) ~  log(gdp_pc) + lag(quota, 2) + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr_cont[["ln(TFR) Prim. Educ."]] <- lm_robust(
  log(TFR_WDI) ~  log(gdp_pc) + lag(quota, 2) + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_tfr_cont[["ln(TFR) Full"]] <- lm_robust(
  log(TFR_WDI) ~  log(gdp_pc) + lag(quota, 2) + HEA_EXP + EDU_PRIM_WDI + cpia_gender,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_control[["ln(TFR)"]] <- models_tfr_cont[["ln(TFR) Full"]]

modelsummary(
  models_tfr_cont, 
  stars = T, 
  title = "ln(Total Fertility Rate) with Controls",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  kable_styling(full_width = T) %>% 
  column_spec(1, width="60pt") %>% save_kable("tables/additional/TFR_controls.tex")
```

## Complete

```{r tfr complete}
tfr_comp <- list()

tfr_comp[["TFR"]] <- models_tfr[["(6)"]]
tfr_comp[["ln(TFR) Base"]] <- models_tfr[["(9)"]]
tfr_comp[["ln(TFR) Cont. 1"]] <- models_tfr_cont[["ln(TFR)  Gender Policy"]]
tfr_comp[["ln(TFR) Cont. 2"]] <- models_tfr_cont[["ln(TFR) Health Expenditure"]]
tfr_comp[["ln(TFR) Cont. 3"]] <- models_tfr_cont[["ln(TFR) Prim. Educ."]]
tfr_comp[["ln(TFR) Full"]] <- models_tfr_cont[["ln(TFR) Full"]]
tfr_comp[["IV TFR"]] <- models_iv[["(6)"]]
tfr_comp[["IV ln(TFR)"]] <- models_iv_ln[["(6)"]]

modelsummary(
  tfr_comp,
  fmt = 2,
  stars = T, 
  title = "Total Fertility Rate (with country weights exlcuding China and India) \\label{tab:tfr}",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  kable_styling(full_width = F) %>% 
  footnote("All models include country and year fixed effects. Standard errors clustered by country, and 95% confidence intervals are presented in square brackets.") %>% 
  column_spec(1, width="60pt")  %>% save_kable("tables/TFR_complete.tex")

```

# Child Mortality

## Base

```{r i5m base}
models_i5m <- list()

models_i5m[["(1)"]] <- lm_robust(
  women_parliament ~ log(gdp_pc) + lag(quota, 1),
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m[["(2)"]] <- lm_robust(
  women_parliament ~ log(gdp_pc) + lag(quota, 1),
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m[["(3)"]] <- lm_robust(
  women_parliament ~ log(gdp_pc) + lag(quota, 1),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m[["(4)"]] <- lm_robust(
  I5M_WDI ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m[["(5)"]] <- lm_robust(
  I5M_WDI ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m[["(6)"]] <- lm_robust(
  I5M_WDI ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m[["(7)"]] <- lm_robust(
  log(I5M_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m[["(8)"]] <- lm_robust(
  log(I5M_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m[["(9)"]] <- lm_robust(
  log(I5M_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

#### Style of the Table
rows <- tribble(~term,             ~first,  ~sec, ~th, ~four, ~five, ~six, ~sev, ~eig, ~nin,
                'Exclude CN + IN',   ' ' ,   '*', '*',   ' ',   '*',  '*',  ' ',  '*', '*',
                'Population Weights',' ' ,   ' ', '*',   ' ',   ' ',  '*',  ' ',  ' ', '*')

attr(rows, 'position') <- c(7,8)

modelsummary(
  models_i5m, 
  fmt = 2,
  stars = T, 
  title = "Child Mortality before 5",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  add_rows = rows,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  add_header_above(c(" " = 1, "% of Women in Parliament" = 3, "Child Mortality" = 3, "ln(Child Mortality)" = 3)) %>% 
  kable_styling(full_width = T) %>% 
  column_spec(1, width="60pt") %>% save_kable("tables/additional/I5M_base.tex")
```

## Controls

```{r i5m controls}
models_i5m_cont <- list()

models_i5m_cont[["ln(I5M)"]] <- lm_robust(
  log(I5M_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_cont[["ln(I5M) Gender Policy"]] <- lm_robust(
  log(I5M_WDI) ~  log(gdp_pc) + lag(quota, 2) + cpia_gender,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_cont[["ln(I5M) Health Expenditure"]] <- lm_robust(
  log(I5M_WDI) ~  log(gdp_pc) + lag(quota, 2) + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_cont[["ln(I5M) Prim. Educ"]] <- lm_robust(
  log(I5M_WDI) ~  log(gdp_pc) + lag(quota, 2) + EDU_PRIM_WDI,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_cont[["ln(I5M) Full"]] <- lm_robust(
  log(I5M_WDI) ~  log(gdp_pc) + lag(quota, 2)  + EDU_PRIM_WDI + HEA_EXP+ cpia_gender,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_cont[["ln(I5M) no CPIA Gender"]] <- lm_robust(
  log(I5M_WDI) ~  log(gdp_pc) + lag(quota, 2)  + EDU_PRIM_WDI+ HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_control[["ln(I5M)"]] <- models_i5m_cont[["ln(I5M) Full"]]

modelsummary(
  models_i5m_cont, 
  fmt = 2,
  stars = T, 
  title = "ln(Child Mortality before 5)",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  kable_styling(full_width = T) %>% 
  column_spec(1, width="60pt") %>% save_kable("tables/additional/I5M_controls.tex")
```

## I5M complete

```{r i5m complete}
i5m_comp <- list()

i5m_comp[["I5M"]] <- models_i5m[["(6)"]]
i5m_comp[["ln(I5M) Base"]] <- models_i5m[["(9)"]]
i5m_comp[["ln(I5M) Cont. 1"]] <- models_i5m_cont[["ln(I5M)  Gender Policy"]]
i5m_comp[["ln(I5M) Cont. 2"]] <- models_i5m_cont[["ln(I5M) Health Expenditure"]]
i5m_comp[["ln(I5M) Cont. 3"]] <- models_i5m_cont[["ln(I5M) Prim. Educ."]]
i5m_comp[["ln(I5M) Full"]] <- models_i5m_cont[["ln(I5M) Full"]]
i5m_comp[["IV I5M"]] <- models_iv[["(9)"]]
i5m_comp[["IV ln(I5M)"]] <- models_iv_ln[["(9)"]]


modelsummary(
  i5m_comp,
  fmt = 2,
  stars = T, 
  title = "Child Mortality before 5 (with country weights exlcuding China and India)",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  kable_styling(full_width = T) %>% 
  column_spec(1, width="60pt") %>% save_kable("tables/I5M_complete.tex")
```

## Male and Female

```{r i5m fm}
models_i5m_fm <- list()

models_i5m_fm[["ln() Base"]] <- lm_robust(
  log(I5M_F_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_fm[["ln() Full"]] <- lm_robust(
  log(I5M_F_WDI) ~  log(gdp_pc) + lag(quota, 2)  + EDU_PRIM_F_WDI +
    EDU_PRIM_M_WDI + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_fm[["IV"]] <- iv_robust(
  I5M_F_WDI ~ log(gdp_pc) + EDU_PRIM_F_WDI + EDU_PRIM_M_WDI + 
    HEA_EXP + lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_F_WDI +
    EDU_PRIM_M_WDI + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_fm[["IV ln()"]] <- iv_robust(
  log(I5M_F_WDI) ~ log(gdp_pc) + EDU_PRIM_F_WDI + EDU_PRIM_M_WDI + 
    HEA_EXP + lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_F_WDI +
    EDU_PRIM_M_WDI + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")


### Male Section
models_i5m_fm[["ln() Base "]] <- lm_robust(
  log(I5M_M_WDI) ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")#MALE encoded by space (to be able to plot a nice table)

models_i5m_fm[["ln() Full "]] <- lm_robust(
  log(I5M_M_WDI) ~  log(gdp_pc) + lag(quota, 2) +  EDU_PRIM_F_WDI +
    EDU_PRIM_M_WDI + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0") #MALE encoded by space (to be able to plot a nice table)

models_i5m_fm[["IV "]] <- iv_robust(
  I5M_M_WDI ~ log(gdp_pc) + EDU_PRIM_F_WDI + EDU_PRIM_M_WDI + 
    HEA_EXP + lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_F_WDI +
    EDU_PRIM_M_WDI + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")#MALE encoded by space (to be able to plot a nice table)

models_i5m_fm[["IV ln() "]] <- iv_robust(
  log(I5M_M_WDI) ~ log(gdp_pc) + EDU_PRIM_F_WDI + EDU_PRIM_M_WDI + 
    HEA_EXP + lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_F_WDI +
    EDU_PRIM_M_WDI + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0") #MALE encoded by space (to be able to plot a nice table)

modelsummary(
  models_i5m_fm, 
  fmt = 2,
  stars = T, 
  title = "Female and Male Child Mortality before 5 \\label{tab:i5m_fm}",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "Female Child Mortality before 5" = 4, "Male Child Mortality before 5" = 4)) %>%
  footnote("All models include country and year fixed effects. Standard errors clustered by country, and 95% confidence intervals are presented in square brackets.") %>% 
  column_spec(1, width="60pt") %>% save_kable("tables/I5M_fm.tex")
```


## Difference
```{r i5m diff}
models_i5m_fm_diff <- list()

models_i5m_fm_diff[["Base"]] <- lm_robust(
  I5M_M_WDI - I5M_F_WDI ~  log(gdp_pc) + lag(quota, 2),
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_fm_diff[["ln()"]] <- iv_robust(
  log(I5M_M_WDI-I5M_F_WDI) ~ log(gdp_pc) + EDU_PRIM_F_WDI + EDU_PRIM_M_WDI + 
    HEA_EXP + lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_F_WDI +
    EDU_PRIM_M_WDI + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_fm_diff[["IV"]] <- iv_robust(
  I5M_M_WDI-I5M_F_WDI ~ log(gdp_pc) + EDU_PRIM_F_WDI + EDU_PRIM_M_WDI + 
    HEA_EXP + lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_F_WDI +
    EDU_PRIM_M_WDI + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

models_i5m_fm_diff[["IV ln()"]] <- iv_robust(
  log(I5M_M_WDI-I5M_F_WDI) ~ log(gdp_pc) + EDU_PRIM_F_WDI + EDU_PRIM_M_WDI + 
    HEA_EXP + lag(women_parliament, 1) | lag(quota,2) + log(gdp_pc) + EDU_PRIM_F_WDI +
    EDU_PRIM_M_WDI + HEA_EXP,
  clusters = dhscc3,
  data = df_w, 
  weights = pop,
  fixed_effects = year + dhscc3,
  se_type = "CR0")

modelsummary(
  models_i5m_fm_diff, 
  fmt = 2,
  stars = T, 
  title = "Male minus Female Child Mortality before 5 \\label{tab:i5m_diff}",
  coef_rename = coef_map,
  statistic = stat_map,
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  kable_styling(full_width = T) %>% 
  footnote("All models include country and year fixed effects. Standard errors clustered by country, and 95% confidence intervals are presented in square brackets.") %>% 
  column_spec(1, width="60pt")  %>% save_kable("tables/I5M_fm_diff.tex")
```


# All models

```{r all (also iv) models with controls}
all_models = append(models_control, iv_models)

modelsummary(
  all_models, 
  fmt = 3,
  stars = T, 
  coef_rename = coef_map,
  statistic = stat_map,
  title = " Full Diff in Diff and IV regressions (with country weights exlcuding China and India) \\label{tab:all}",
  coef_omit = "Intercept",
  gof_map = gm_map,
  escape = FALSE,
  format = "latex",
  conf_level = .95,
  gof_omit = "se_type") %>% 
  kable_styling(full_width = T) %>% 
  footnote("All models include country and year fixed effects. Standard errors clustered by country, and 95% confidence intervals are presented in square brackets.") %>% 
  column_spec(1, width="60pt") %>% save_kable("tables/All.tex")
```

